|

### 2025-05-05 doc/abstract.tex
Adjust abstract&titlepage to uni guidelines

This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide infrastructure for open science-oriented empirical projects. Leveraging data from the CRSP and Compustat databases, alongside Worldscope and Datastream via WRDS, this repository showcases a reproducible workflow integrating Python scripts for data preparation, analysis, and visualization. Integrating multiple databases adds complexity, requiring a detailed understanding of their structures and careful scripting to extract, align, and analyze data effectively.

The project replicates and extends Ball and Shivakumar (2008) to analyze the informativeness of quarterly earnings announcements and their contribution to share price movements, highlighting their critical role in investment decisions and impact on investors and analysts. Key tasks include replicating and comparing original results, extending the analysis to 2007–2023, and applying the methodology to a non-U.S. country. The project also documents research design choices, discusses variations between original and reproduced results, and provides insights into earnings informativeness across different timeframes and jurisdictions. Additionally, it sketches a research design for a non-archival study to evaluate the paper’s findings. This code base, adapted from TREAT, demonstrates how the template applies to this project and serves as a structured guide for reproducible empirical research in accounting.

>>>>

This thesis examines how much new information is conveyed in quarterly earnings announcements, replicating and extending the study by Ball and Shivakumar (2008). Using a reproducible workflow based on the TRR 266 Template, I analyze U.S. and Canadian data from 1972 to 2023, applying an event-study design to assess the explanatory power of earnings windows on annual stock returns. The findings show that earnings informativeness varies across time and jurisdictions, with evidence suggesting institutional factors influence market reactions. A non-archival survey design is also proposed to explore investor perceptions, enriching the archival analysis with complementary behavioral insights.
